ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
fixing typo
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

ESBMC-GPU builds on top of ESBMC, which is an open source context-bounded model checker based on SMT solvers for ANSI-C/C$++$ programs~\cite{cordeiro:2011,cordeiro:2012}, and adds four essential models, as described below.

>>>>

ESBMC-GPU is built on top of ESBMC, which is an open source context-bounded model checker based on SMT solvers for ANSI-C/C$++$ programs~\cite{cordeiro:2011,cordeiro:2012}, and adds four essential models, as described below.
